Stat 534 Project: \\ Extrapolation from Poisson Process Intensity Surface Models

### 2017-03-23 project/pres.rnw
Getting into heavy-duty computation.

<<polyfit, warning = FALSE, cache = TRUE>>=
ex_fit1 <- ppm(ex_ppp ~ x + y)
ex_Q <- quad(data = ex_ppp,
             dummy = as.ppp(rbind(
               data.frame(vertices(Window(ex_ppp))),
               do.call(rbind, lapply(unique(ex_path$x), function(x){
                 return(data.frame(
                   x = x, y = seq(min(ex_path$y), max(ex_path$y),
                                  length.out = 128)
                 ))}))), W = Window(ex_ppp)))

@@

@@

\item Dummy points outside the actual window are discarded

@@

\item I place 128 evenly-spaced dummy points along each transect

\item \Sexpr{prettyNum(ex_Q$dummy$n, big.mark = ',')} are used

>>>>

<<polyfit, warning = FALSE, cache = TRUE>>=
ex_fit1 <- ppm(ex_ppp ~ x + y)
ex_Q <- quad(data = ex_ppp, dummy = runifpoint(500000, Window(ex_ppp)))

@@

\vspace{-11pt}
\begin{itemize}

@@

@@

\item I draw \Sexpr{prettyNum(ex_Q$dummy$n, big.mark = ',')} points from a
uniform distribution on the observed region

\item \textcite{wartonshepherd} recommend using enough dummy points that the
maximized log-likelihood converges
